The role of advection versus diffusion in intraventricular transport

### 2025-02-15 paper/main.tex
add dolfinx citation

The numerical solution schemes for the Stokes equations and the
advection-diffusion equation were implemented and solved numerically with DOLFINx,
the Python interface of the finite element software
FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with
petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
linear systems resulting from the discretized Stokes equations.
For the discretized advection-diffusion equation, we used an iterative
linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
preconditioning~\cite{Jacobi1845UeberGleichungen}.
Numerical experiments verified the accuracy of the model implementation
(\Cref{sec:appB_verification}). The simulation code is openly
available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.

>>>>

The numerical solution schemes for the Stokes equations and the
advection-diffusion equation were implemented and solved numerically with DOLFINx~\cite{dolfinx2023preprint},
the Python interface of the finite element software
FEniCSx, with
petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
linear systems resulting from the discretized Stokes equations.
For the discretized advection-diffusion equation, we used an iterative
linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
preconditioning~\cite{Jacobi1845UeberGleichungen}.
Numerical experiments verified the accuracy of the model implementation
(\Cref{sec:appB_verification}). The simulation code is openly
available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
